---
title: "Example workflow using `litreview`"
format: html
---

```{r}
#| echo: false
lapply(list.files("R", full.names = TRUE), source)
```

First, we start off using the `call_oa_api` function to send our DOI to the unpaywall API. It's important to provide your email address, otherwise you run the risk of being blacklisted.

```{r}
oa_api_results <- call_oa_api("10.1186/s13063-023-07338-5","your@email.com")
```

Once we've got a response from the API, we then check for candidate URLs that might point us to a pdf file for the DOI.

```{r}
pdf_locations <- get_possible_locations(oa_api_results, "pdf")
pdf_locations
```

With these locations, we can try to download the pdf directly

```{r}
try_pdf_location(pdf_locations[[1]])
try_pdf_location(pdf_locations[[2]])
try_pdf_location(pdf_locations[[3]])
```

No luck with the first two, but the third one succeeds.

If none of the pdf locations worked, we can also try our luck using webpages and scraping the HTML

```{r}
html_locations <- get_possible_locations(oa_api_results, "html")
html_locations
```

